---
title: "Incubation_Analytics"
author: "Akin"
date: "October 14, 2016"
output: html_document
---


## Fetching Data
```{r fetching data1}
incubation <- read.csv("./incpreincideasubmissions/Incubation Application-report (Edited) (1).csv",
                       stringsAsFactors = FALSE)
```

## ANALYSIS OF INCUBATION
```{r echo=FALSE}
options(warn = -1,show.error.messages = F)
```
This report processes the submissions received from the incubation-idea submission. The various fieds collected are listed below:
```{r variables}
names(incubation)
```
The report makes give some certain insights derivable from the data collected from the respondents

## Preparing Workspace

```{r preparing workspace, echo=FALSE, message=FALSE}
rm(list = ls())
if("dplyr" %in% row.names(installed.packages()) == FALSE){install.packages("dplyr")}
if ("ggplot2" %in% row.names(installed.packages()) == FALSE){install.packages("ggplot2")}
if ("ggmap" %in% row.names(installed.packages()) == FALSE){install.packages("ggmap")}
if ("maptools" %in% row.names(installed.packages()) == FALSE){install.packages("maptools")}
if ("maps" %in% row.names(installed.packages()) == FALSE){install.packages("maps")}
if ("rgeos" %in% row.names(installed.packages()) == FALSE){install.packages("rgeos")}
library(dplyr)
library(ggplot2)
library(ggmap)
library(maptools)
library(maps)
library(rgeos)
setwd("c:/Users/AROOGZ/Documents/My Works/WORK - CcHUB/Inc and Pre-Inc/")
```


## Fetching Data
```{r fetching data}
incubation <- read.csv("./incpreincideasubmissions/Incubation Application-report (Edited) (1).csv",
                       stringsAsFactors = FALSE)
```


## Preprocessing
```{r }
incubation_edit <- unique(incubation)
  
#function to get the equivalent willingness
getwilling <- function(code){
  if (code == 1){
    return("willing")
  }
  else{
    return("notwilling")
  }
}

incubation_edit <- mutate(incubation, willingness= lapply(incubation$Are.you.willing.to.move.to.Lagos.for.next.6.months., getwilling))

#convert dates
incubation_edit <- mutate(incubation_edit, 
                          applicationStart = as.Date(incubation_edit$Start.Date..UTC., "%m/%d/%Y %H:%M"),
                          applicationEnd = as.Date(incubation_edit$Submit.Date..UTC., "%m/%d/%Y %H:%M"))

#get the time taken to fill the form
formFilling <- vector()
for (i in seq(length(incubation_edit$Submit.Date..UTC.))){
  timediff <- difftime(incubation_edit$applicationEnd[i], incubation_edit$applicationStart[i], units = "days")
  timediff <- as.numeric(timediff)
  formFilling <- c(formFilling, timediff)
  
}
incubation_edit <- mutate(incubation_edit, formFillingTime= formFilling)

incubation_edit <- mutate(incubation_edit, submissionMonth = months(incubation_edit$applicationEnd, abbreviate = T))
incubation_edit <- mutate(incubation_edit, willingness= as.character(incubation_edit$willingness))

#improve on location
incubation_edit <- mutate(incubation_edit, 
                          location= paste(incubation_edit$Current.location, 
                                          "Nigeria"))
```


## Showing the Visuals
```{r total submission}
par(mar = c(0,0,0,0))
plot(c(0, 1), c(0, 1), ann = F, 
     bty = 'n', type = 'n', xaxt = 'n', yaxt = 'n')

text(x=0.5, y=0.5, paste("TOTAL NUMBER OF UNIQUE SUBMISSIONS\n",
                          as.character(nrow(incubation_edit))), 
     cex = 1.6, col = "black")
```

We had an almost neglible number of persons unwilling to come to Lagos of the total number of idea submissions. This is obvious from the plot below derived from a yes or no response as given by the `Are.you.willing.to.move.to.Lagos.for.next.6.months.`

## Willingness to Come to Lagos
```{r willingness}
#willingness to come
will <- as.data.frame(table(incubation_edit$willingness, 
                                   dnn = c("willingness")))

ggplot(will, aes(will$willingness, 
                        will$Freq))+geom_bar(stat = "identity",
                                                    #col = "red",
                                                    #fill = "blue",
                                                    alpha = 0.4)+labs(x =
      "willingness to come to Lagos", y = "Number of Submissions")+ggtitle(
        "The Willingness to Come To Lagos for 6 Months")+geom_text(
          aes(label = Freq), size = 5, vjust= "middle")+theme_bw()
```

Majority of the submissions received come from within Lagos (as would normally be expected) and largely, the Southwest with just a few more outside these areas such as the middle-belt and the South-South. Submissions were not recieived from the Northern Part of the Country.

The following visualisation helps to show this distribution. The response to the `Current.location` field has been used to generate reasonably approximate locations for the plotted points. The deeper blue colours signifies more submissions from a given location

## Locations
```{r location}

#loc <- incubation_edit$location
#loc.code <- geocode(location = loc)

loc.code <- read.csv("./incubation_locations.csv", stringsAsFactors = F)
mp <- NULL
mapWorld <- borders("world", regions = "Nigeria", colour="gray50", fill="gray50") # create a layer of borders
mp <- ggplot() +   mapWorld

#Now Layer the cities on top
mp <- mp+ geom_point(aes(x=loc.code$lon, y=loc.code$lat) ,color="blue", size=3, alpha= 0.3) 
mp + coord_cartesian(ylim = c(0,15), xlim = c(0, 20))+labs(x= "", 
                                                           y= "", title= "Distribution of the Submission Clusters Across Nigeria")+theme_bw()

```

## Moving Forward

Effort is still being made to deriv more information on the data. However, the following are my recommendations:

- I will suggest that more variables be collected, such as;

  + Age

  + level of Education

  These will further help gain insights into the idea submission as well  as the individuals, providing us with potentially useful information on the distribution of respondents

- Also the use of categorical variables where applicable will ease classification

 



